\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=2cm]{geometry}
\usepackage{placeins}

\titleformat{\subsection}
{\bfseries\large}
{}
{0em}
{}

\title{Meeting Minutes}
\date{13.01.21}
\begin{document}
\maketitle

\begin{center}
    \begin{tabular}{ | l | p{14cm} |}
    \hline
    Members Present & Ivan, Darius \\ \hline
    Creator         & Ivan Kalashnikov \\ \hline
    Date            & 13.01.21 \\ \hline
    Time            & 18:00 \\ \hline
    \end{tabular}
\end{center}

\subsection{Absences}

Stevens (Was not present due to nature of discussion. The scope of the discussion was centred between Ivan and Darius tasks only)

\subsection{Agenda}

Database - The discussion was made around our implantation of the user class and how the user class would intercommunicate with song lists \& movie lists. 

\subsection{Meeting Notes}
\begin{itemize}
	\item User class: deciding how to implement the user class between a monolithic database option or a more decentralised and implement a database for each user. 
	\item Encryption: What approach are we taking to encrypt our application and users 
\end{itemize}

\subsection{Meeting Summary}

We concluded that the \textit{users} will have a small database for the user, as this approach we concluded is cuts down the constraints for us to implement, improves application resilience as it allows for breakage of small databases that doesn't take away function from the overall application, and improves security as the application will automatically encrypt the users database, with the user only retaining the private key and sharing the public key with the server for \textit{decryption}.

The discussion about \textbf{Encryption} was easier in the sense that we both agree on the same implementation. we both agree with implementation a GPG style of encryption, an industry standard in approach with applications such as telegram and signal having similar approaches. Every new user will generate a \textit{Public} and \textit{Private} key, the user will share the public key with us, decrypting their content. The downside is that they need to keep the \textit{Private} key, once lost is unrecoverable.    

\subsection{Tasks Completed (Since Last meeting)}
See previous meeting for the last as it still needs to be completed and due in.
\subsection{Task to be Completed (For next meeting) }
Tasks listed to be completed and reviewer assigned
\begin{center}
    \begin{tabular}{|p{9cm}|l|l|l|l|}
    \hline
    Task Name and Description & Completed By & Date & Reviewed By & Completed \\ \hline
	    Users database &Ivan \& Darius & 13.01.21&Stevens& NA           \\ \hline
    \end{tabular}
    \end{center}
No more added as more tasks need to be completed

\end{document}
